---
title: "simpleRegress"
author: "Jeanette Serrano"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

When we used the NECK to predict the LENGTH it looks about a straight line, the R squared value is about 0.75. 

```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

We will try HEADLEN to predict LENGTH. Tried a few variables and this one appeared to be the best towards adjusted R squared. 


```{r}
headlength <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(headlength)
summary.lm(headlength)
```

```{r}
new <- data.frame(HEADLEN=c(17,22,26))
predict(headlength,new)
predict(headlength,new,se.fit=TRUE)
```






## now predict the length of a bear who has a neck of 17, 22 and 26




## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

